Updating the Feature Function Framework \titlelinebreak{} in the Moses Decoder

### 2013-07-18 mt-marathon.2013/PBML_article.tex
ken's suggestions

cdec also supports an arbitrary number of passes, feature functions can be assigned to a particular
pass.

@@

\subsection{cdec}
cdec eschews Moses' dense and sparse hybrid approach and implement only sparse maps. Dense features can still be modelled in the framework as sparse features, whose name are suffixed with indices.

To improve speed and memory usage, hypotheses only store deltas of feature differences with antecedent hypotheses.

@@

Hypotheses only retain the weighted sum of the feature scores, . The individual score components are not stored unless required, for example, in the n-best list. The intuition behind this approach is that the score breakdown is only required in some situations. In most other circumstances, they can be traded for better speed and lower memory consumption.

>>>>

cdec also supports an arbitrary number of passes, feature functions can be assigned to a particular
pass. cdec's multi-pass strategy for feature function evaluation build on its course-to-fine framework.

@@

\subsection{cdec}
cdec eschews Moses' dense and sparse hybrid approach and implement only sparse maps. Dense features can still be modelled in the framework as sparse features, whose name are suffixed with indices. However, it optimizes sparse feature handling by using different data structures, depending on the number of feature scores.

Also, to improve speed and memory usage, hypotheses only store features deltas with respect to antecedent hypotheses.

@@

Hypotheses only retain the weighted sum of the feature scores. The individual score components are not stored unless required, for example, in the n-best list. The intuition behind this approach is that the score breakdown is only required in some situations. In most other circumstances, they can be traded for better speed and lower memory consumption.
